Wavelets

### 2019-03-02 Chlorophyll_a .Rmd
updated
progress

# With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <- daily_chloro_match %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>% 
  dplyr::group_by(combi, lon, lat) %>% 
  tidyr::nest() %>% 
  dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
                       climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
                       maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  dplyr::select(-data) %>% 
  tidyr::unnest() %>% 
  select(-doy, -seas, -thresh)

ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

>>>>

# With the chloro pixels filter, it is now faster to create the daily data
daily_chloro_data <- daily_chloro_match %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  dplyr::group_by(combi, lon, lat, date) %>% 
  dplyr::summarise(chloro = mean(chloro, na.rm = TRUE)) %>% 
  dplyr::group_by(combi, lon, lat) #%>% 
  # tidyr::nest() %>% 
  # dplyr::mutate(clims = purrr::map(data, ts2clm, x = date, y = chloro,
  #                      climatologyPeriod = c("2002-07-13", "2018-12-04"), # This doesn't mean anything, but the function needs it to work
  #                      maxPadLength = 8)) %>% # Adjust maxPadLength = X for longer interpolation
  # dplyr::select(-data) %>% 
  # tidyr::unnest() %>% 
  # select(-doy, -seas, -thresh)
s
#Plotting daily data
# ggplot(daily_chloro_data, aes(x = date, y = chloro)) +
#   geom_line() +
#   facet_wrap(~combi, ncol = 1)

# Plotting only years 2014-2015
daily_chloro_data_tester <- daily_chloro_data %>% 
  filter(year(date) %in% seq(2014, 2015))

rough_plot <- ggplot(daily_chloro_data_tester, aes(x = date, y = chloro)) +
  geom_line() +
  facet_wrap(~combi, ncol = 1)

### 2019-03-02 wavelets.Rmd
progress

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/overlap_ts.RData")
load("~/Documents/Masters_2019/MastersProject/Data/insitu_MUR.RData")
load("~/Documents/Masters_2019/MastersProject/Data/insitu_OISST.RData")
load("~/Documents/Masters_2019/MastersProject/Data/insitu_G1SST.RData")
load("~/Documents/Masters_2019/MastersProject/Data/insitu_K10.RData")
```

@@

save(SACTN_fyears, file = "Data/temp_2014_2015/SACTN_fyears.RData")
save(MUR_fyears, file = "Data/temp_2014_2015/MUR_fyears.RData")
save(OISST_fyears, file = "Data/temp_2014_2015/OISST_fyears.RData")
save(G1SST_fyears, file = "Data/temp_2014_2015/G1SST_fyears.RData")
save(K10_fyears, file = "Data/temp_2014_2015/K10_fyears.RData")
```

@@

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
# SACTN_fyears <- SACTN_fyears %>% 
#   dplyr::rename(temp = insitu_temp)

@@

# temp.d <- temp.d(df = SACTN_fyears) 
# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
temp.d <- temp.d(df = K10_fyears)

@@

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```

>>>>

```{r}
load("Data/overlap_ts.RData")
load("Data/insitu_MUR.RData")
load("Data/insitu_OISST.RData")
load("Data/insitu_G1SST.RData")
load("Data/insitu_K10.RData")
```

@@

# save(SACTN_fyears, file = "Data/temp_2014_2015/SACTN_fyears.RData")
# save(MUR_fyears, file = "Data/temp_2014_2015/MUR_fyears.RData")
# save(OISST_fyears, file = "Data/temp_2014_2015/OISST_fyears.RData")
# save(G1SST_fyears, file = "Data/temp_2014_2015/G1SST_fyears.RData")
# save(K10_fyears, file = "Data/temp_2014_2015/K10_fyears.RData")
```

@@

# When doing a wavelet analyses on the SACTN dataset the "insitu_temp" column needed to be renamed to "temp" for the rest of the code to run. The rest of this code is kept constant for each of the datasets (Remotely-sensed SST and In-situ seawater temperature)
SACTN_fyears <- SACTN_fyears %>%
  dplyr::rename(temp = insitu_temp)

@@

temp.d <- temp.d(df = SACTN_fyears) 
# temp.d <- temp.d(df = MUR_fyears) 
# temp.d <- temp.d(df = OISST_fyears)
# temp.d <- temp.d(df = G1SST_fyears) 
# temp.d <- temp.d(df = K10_fyears)

@@

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/new",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```

## Examining seasonal upwelling

Creating a seasonal column. Allowing me to compare the intensity/duration of upwelling on a seasonal basis. This should to be repeated for each of the sites within each of the datasets (SACTN, MUR, OISST, G1SST and K10). The code bellow needs to be edited. Here I only focused on Port Nolloth within the SACTN dataset.

```{r}
load("Data/temp_2014_2015/G1SST_fyears.RData")
load("Data/temp_2014_2015/K10_fyears.RData")
load("Data/temp_2014_2015/MUR_fyears.RData")
load("Data/temp_2014_2015/OISST_fyears.RData")
load("Data/temp_2014_2015/SACTN_fyears.RData")

seasonal_col <- function(df){
  temp_data <- df %>% 
    mutate(month = month(date, abbr = T, label = T),
           year = year(date)) %>% 
    group_by(site, month, year) %>% 
     mutate(season = ifelse(month %in% c("Jan", "Feb", "Mar"), "Summer",        
                           ifelse(month %in% c("Apr", "May", "Jun"), "Autumn",
                                ifelse(month %in% c("Jul", "Aug", "Sep"), "Winter",
                                       ifelse(month %in% c("Oct", "Nov", "Dec"), "Spring","Error")))))
  return(temp_data)
}

SACTN_seasonal <- seasonal_col(df = SACTN_fyears)
MUR_seasonal <- seasonal_col(df = MUR_fyears)
OISST_seasonal <- seasonal_col(df = OISST_fyears)
G1SST_seasonal <- seasonal_col(df = G1SST_fyears)
K10_seasonal <- seasonal_col(df = K10_fyears)

# save(SACTN_seasonal, file = "Data/temp_2014_2015/SACTN_seasonal.RData")
# save(MUR_seasonal, file = "Data/temp_2014_2015/MUR_seasonal.RData")
# save(OISST_seasonal, file = "Data/temp_2014_2015/OISST_seasonal.RData")
# save(G1SST_seasonal, file = "Data/temp_2014_2015/G1SST_seasonal.RData")
# save(K10_seasonal, file = "Data/temp_2014_2015/K10_seasonal.RData")

load("Data/temp_2014_2015/SACTN_seasonal.RData")
load("Data/temp_2014_2015/MUR_seasonal.RData")
load("Data/temp_2014_2015/OISST_seasonal.RData")
load("Data/temp_2014_2015/G1SST_seasonal.RData")
load("Data/temp_2014_2015/K10_seasonal.RData")
```

A seasonal plotting representing the sea surface temperature for 2014 and 2015

```{r}
PN_14 <- SACTN_seasonal %>% 
  filter(site == "Port Nolloth") %>% 
  filter(year == 2014 )

PN_15 <- SACTN_seasonal %>% 
  filter(year == 2015 )
  # filter(site == "Port Nolloth") %>% 
  # filter(year == 2015 )

combined_seasonal <- function(df){
  plot <- df %>% 
    ggplot(aes(x = date, y = insitu_temp)) +
    geom_line() +
    facet_wrap(~season, ncol = 2, nrow = 2) +
    theme_bw()
}

combined_seasonal_2014 <- combined_seasonal(df = PN_14)
combined_seasonal_2015 <- combined_seasonal(df = PN_15)
combined_PortNolloth <- ggarrange(combined_seasonal_2014, combined_seasonal_2015)

# ggsave(plot = combined_PortNolloth, filename = "Figures/combined_PortNolloth.png")
```

Creating a wavelet analyses for the year 2015. This code creates a plot per season.

```{r}
seasonal_PN_15 <- PN_15 %>% 
  dplyr::rename(temp = insitu_temp)

temp.d <- function(df){
temp.d <- df %>% 
  dplyr::group_by(site, date, season) %>% 
  dplyr::summarise(temp = mean(temp, na.rm = T)) %>%
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(season, site, no, temp)
}

temp.d <- temp.d(df = seasonal_PN_15)

temp.d <- temp.d %>% 
  select(season, site, no, temp)

prewhite_fun <- function(x) {
  df <- x[, 3:4]
  out <- prewhiteAR(df, order = 3, method = "mle", aic = TRUE,
             genplot = FALSE, verbose = FALSE)
  colnames(out) <- c("no", "temp")
  return(out)
  }
PN_prewhite <- as.tibble(ddply(temp.d, .(site, season), prewhite_fun))

temp_seasonal <- ggplot(temp.d, aes(x = date, y = temp)) +
  geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ season, nrow = 4) +
  theme_bw()

PN_wave <- dlply(temp.d, .(site, season), wl.fun)

for (i in 1:length(PN_wave)) {
  attributes(PN_wave[[i]]) <- c(attributes(PN_wave[[i]]), ref = names(PN_wave)[i])
}
# x <- PN_wave[[3]]
plot_fun <- function(x, plot_name = attributes(x)$ref) {
  png(filename = paste0("Figures/new",plot_name,"_wavelets.png"),
      width = 800, height = 600, units = "px", pointsize = 12, bg = "white")
  wt.image(x, siglvl = 0.05, col.contour = "black", color.key = "quantile",
           timelab = "Days", verbose = FALSE, useRaster = TRUE,
           periodlab = "Period", lwd = 1, graphics.reset = FALSE,
           main = plot_name)
  dev.off()
}
ldply(PN_wave, plot_fun)
```
